	\section{Pipeline spills: qualitative insights}
	\begin{paracol}{2}
	\begin{itemize}
		\item Research setting
		\switchcolumn Similar to \citet{Howard-Grenville2017}, take this opportunity to give a little bit of background info, along with relevant information on data sources etc.
		\switchcolumn*
		
			\subitem Pollution of ecosystems from pipeline spills
			\subitem Damages to public health from pipeline spills
		\switchcolumn Provide explanation of why pipeline spills are an issue in the realm of management of natural resources. 
		\switchcolumn*
		
		\item Learning most unambiguous where failure (spill) occurred \citep{Madsen2010}
			\subitem Analyze recent pipeline spills \& response
		\switchcolumn Justify the approach of the qualitative section to cover incidents through learning literature.
		\switchcolumn*
		
		\item NTSB
			\switchcolumn Use opportunity to start introducing institutional context
			\switchcolumn*
	\end{itemize}
	\end{paracol}

	\subsection{Methods}
	\begin{paracol}{2}
	\begin{itemize}
		\item Mixed methods
		\switchcolumn Cite \citet{Montgomery2019} and especially \citet{Vergne2012}--similar structure!
		\switchcolumn*
		
		\item Fifteen significant spills according to five criteria
			\subitem Onshore, crude \& rpp
			\subitem Identified through PHMSA dataset
		\item Sources: NTSB report, PHMSA dataset, archival research for other spills.
		\switchcolumn This is arguably convenience sampling, but because similarly to \citet{Vergne2012} I just use this section to setup my research, a brief qualitative section with less rigorous methodology is probably justified--or at least will not receive too much scrutiny. Alternatively, state that I have continued looking at spills on my list, until themes emerged and I have saturated them. What would be the reference for that?
		\switchcolumn*
		\switchcolumn[0]*
		
		\item Analysis--Gioia method \citep{Gioia2013}
		\switchcolumn Although I have not been following the Gioia, it describes well my approach, moving from concrete to abstract.
		\switchcolumn*		
	\end{itemize}
	\end{paracol}
	
	\subsection{Results}
	\begin{paracol}{2}
	\begin{itemize}
		\item Table with 1st, 2nd, 3rd order.
			\subitem 1st order--sth with technology--tangible
			\subitem 2nd order--sth with systems?
			\subitem 3rd order--sth with complexity?
		\switchcolumn Creating a table with 1st, 2nd, 3rd order themes would also be an easy way to move from technology to complexity. Table would be short though--just as my qual analysis is--fine in my books.
		\switchcolumn*
		
		\item Issue that leads to spills--have reached the point where not individual, concrete problems lead to spills, but complexity of the system
			\subitem Add as hypothesis for quant test?
	\end{itemize}		
	\end{paracol}