
\documentclass[12pt, man, natbib]{apa6}
\usepackage[USenglish]{babel}
\usepackage{setspace}
\usepackage{hyperref}

\title{A Couple of Spills a Year, That's Good? Learning and Greenwashing in the Pipeline Industry}
\shorttitle{Thesis Proposal -- Julian Barg}
\author{Julian Barg\\jbarg.phd@ivey.ca}
\affiliation{Ivey Business School}
\setcitestyle{authoryear, open={()},close={)},citesep={,},aysep=}
\abstract{
	From 2000 to 2020, the standardized spill volume of refined petroleum pipelines has stayed constant at about 10 bbl per billion barrel-miles transported. In contrast, from 1980 to 2000, the standardized spill volume had about halved. This dissertation researches why pipeline operators in the US keep causing oil spills, and how they appease their stakeholders. The dissertation uses two lenses, greenwashing and organizational learning. These lenses reveal why, despite continuous efforts by engineers, the safety record of the industry has stagnated. The greenwashing literature suggests that environmental rhetorics offer many of the same benefits as environmental improvements--especially when stakeholders cannot investigate the claims. The learning literature suggests that it is commonplace for organizational learning to converge at a high level of performance, as observed in the pipeline industry.
	
	The first chapter discusses how pipeline operators keep in check the backlash for the environmental pollution that they cause. Pipeline operators shield themselves from criticism claims of environmental safety that are based pipeline technology. When an operator causes a spill, the operator can point to the latest development in the constant flow of new technology as a remedy for future spills. This chapter and the second chapter use the same data on pipeline spills on 6,147 pipeline spills, and the American pipeline network from 2004-2019. More importantly this chapter further utilizes text data from operators and industry level actors. This research tracks empirically how patterns of greenwashing are diffused in the pipeline industry. This analysis sheds light on the role of technology as a rhetoric that is developed by industry level actors, in this case the American Petroleum Institute and the Association of Oil Pipe Lines.
	
	The second chapter reveals the mechanisms behind the convergence in organizational learning that we have observed in the pipeline industry. The empirical section uses a dataset of 4,929 pipeline spills, and qualitative data on 10 significant pipeline spill. This research reveals that valid learning only occurs in response to the spills that operators experience. For a general theory of learning, the empirical findings suggests that learning converges when the organization or system that learns has developed a high degree of complexity. Because of this complexity, learning in response to triggers such as failures is not sufficient anymore for making aggregate improvements. Learning turns into a perpetual game of whack-a-mole.
	
	The third chapter revisits the theory on organizational learning and develops the concepts of reliability and validity. When learning goes beyond incremental improvements and touches on fundamental assumptions, organizations or industries can break out of their trajectory. However, many learning outcomes that have been thought of as "breakthroughs" have not led to the promised revolutions in the market. Validity and reliability fill an important gap in the literature of learning: even when learning produces sensible and internally consistent insights, these insights are meaningless if they do not serve for the organization to better understand, predict, and control existing problems, limitations, or bottlenecks--that is, if the knowledge is not valid. And valid knowledge still fails to make an impact if it is not reliable, meaning not shared across the organizational members who are to implement the insights.
}

\keywords{greenwashing, organizational learning, industry level, population level, pipeline spills, validity, reliability}

\begin{document}
	
	\maketitle
	
%	\singlespacing

	\tableofcontents
	
	\newpage
	
	\input{sections/introduction}
	
	\input{sections/overview}

	\input{sections/context}

	\input{sections/literature}
	
%	\input{sections/chapters}

	\input{sections/chapter_3}
	
	\input{sections/chapter_1}
	
	\input{sections/chapter_2}
	
%	\input{sections/conclusion}

% 	\input{sections/timeline}

\bibliography{bibliography}

\end{document}